---
title: "Books"
output: pdf_document
author: JianhaoYan 
---

Document assignment
Consider the following situation:
Assignment 1
Haviland Wright September 12, 2018
A sloppy printer produces books with an average of 2 misprints per page. You want to know how many pages have more than k misprints in a book of n pages. Make an n x k table that shows the relationship between the total number of pages in a book and the number of pages with k misprints.
Show and explain your work. Include equations and calculations to teach the reader how to solve the problem. Include an image of a book.
Push your solution to a github repository and submit the url for repository on blackboard. Be sure your repo includes your document as a pdf file and as an RMD file. Include other files needed to recompile your document.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)

```

##For the book of 100 pages

```{r}
num_pages1<-100
data_misprint<-rpois(num_pages1,lambda = 2)
count_k<-c()
set.seed(2018)
for(k in 0:8){
  count<-0
  for(i in 1:num_pages1){
    if(k<data_misprint[i]){
      count<-count+1
    }
   }
  count_k[k]<-count
}
count_k
page100<-data.frame((count_k))

```
##For the book of 150 pages
```{r}
num_pages2<-150
data_misprint<-rpois(num_pages2,lambda = 2)
count_k<-c()
set.seed(2018)
for(k in 0:8){
  count<-0
  for(i in 1:num_pages2){
    if(k<data_misprint[i]){
      count<-count+1
    }
   }
  count_k[k]<-count
}
count_k
page150<-data.frame(count_k)
```
##For the book of 200 pages
```{r}
num_pages3<-200
data_misprint<-rpois(num_pages3,lambda = 2)
count_k<-c()
set.seed(2018)
for(k in 0:8){
  count<-0
  for(i in 1:num_pages3){
    if(k<data_misprint[i]){
      count<-count+1
    }
   }
  count_k[k]<-count
}
count_k
page200<-data.frame(count_k)
```
##For the book of 250 pages
```{r}
num_pages4<-250
data_misprint<-rpois(num_pages4,lambda = 2)
count_k<-c()
set.seed(2018)
for(k in 0:8){
  count<-0
  for(i in 1:num_pages4){
    if(k<data_misprint[i]){
      count<-count+1
    }
   }
  count_k[k]<-count
}
count_k
page250<-data.frame(count_k)
```
##latex
$p=e^{-\lambda}*{-\lambda}/{k!}$
##tabel

```{r}
protable<-cbind(page100,page150,page200,page250)
knitr::kable(protable,row.names=c(1:8),col.names = c("page100","page150","page200","page250"))
```
## image#
```{r}
cover_url = 'https://www.incimages.com/uploaded_files/image/970x450/getty_883231284_200013331818843182490_335833.jpg'
if (!file.exists(cover_file <- 'cover2.jpg'))
download.file(cover_url, cover_file, mode = 'wb')
knitr::include_graphics(if (identical(knitr:::pandoc_to(), 'html')) cover_url else cover_file)
```
